\documentclass[../Paper.tex]{subfiles}
\begin{document}
Population demographic data for the project was acquired from the United Nations
Department of Economic and Social Affairs, Population Division (UN DESA). Measles
seroprevalence data was made available by findings from ESEN2 presented to the World
Health Organization.\\
\\
As previously mentioned, the model will have two age compartments in an effort to
reduce the number of overall dimensions. However, seroprevalence data provided from
the WHO report is given in several age categories, and the appropriate proportion
of measles seronegativity in each age group must be extrapolated. Additionally, the
data collected in the seroepidemiology report were not all done in the same year.
Many countries have not submitted updated data in over 20 years, therefore some
liberty was taken in best estimating these population values. Where possible, 
sensitivity analyses were undertaken to quantify the impact on model results.\\
\\
To extrapolate values to be used in the model, direct standardization was
done using the most recent population age demographics for each country. Two
summary measures were created by summating the weighted rates for each age range
contained in the model compartments. This can be described using the following
equation:\\
  \begin{equation}
    P_{[i,n]} =\sum_{i}^{n}W_{i}\cdot \widehat{p_{i}}
  \end{equation}
  where:\\
  $P_{[i,n]} =$ measles seroprevalence from ages $i$ to $n$, \\
  $W_{i} =$ weight of age group $i$, calculated as the quotient of the population
  of age group $i$ divided by the population in groups $i$ to $n$, and \\
  $\widehat{p_{i}} =$ measles seroprevalence in group $i$ \\
The resulting seroprevalence values are then multiplied by their respective
populations to generate the proportion susceptible and immune in the two age
compartments.
\clearpage
\end{document}